Juilanna's figures for August 29

### 2024-09-10 julianna_figs_Aug29.Rmd
Want to get up to date for workshop

```{r cover CV vs. coral cover}
alltime %>% 
  ggplot(aes(x = coral_cover_hard_mean, y = algae_cover_hard_cv)) +
  geom_point(aes(color = island_side)) +
  facet_wrap(~habitat) +
  geom_smooth(method = "lm") +
  theme_bw()
```

```{r cover CV vs. coral cover CV}
alltime %>% 
  ggplot(aes(x = coral_cover_hard_cv, y = algae_cover_hard_cv)) +
  geom_point(aes(color = island_side)) +
  facet_wrap(~habitat) +
  geom_smooth(method = "lm") +
  theme_bw()
```

>>>>

```{r cover CV vs. coral cover}
alltime %>% 
  ggplot(aes(x = coral_cover_hard_mean, y = macroalgae_cover_hard_cv)) +
  geom_point(aes(color = island_side)) +
  facet_wrap(~habitat) +
  geom_smooth(method = "lm") +
  theme_bw()
```

```{r cover CV vs. coral cover CV}
alltime %>% 
  ggplot(aes(x = coral_cover_hard_cv, y = macroalgae_cover_hard_cv)) +
  geom_point(aes(color = island_side)) +
  facet_wrap(~habitat) +
  geom_smooth(method = "lm") +
  theme_bw()
```
